Comparing fluorometric methods ( in vivo vs extracted) for cyanoHAB monitoring in six Rhode Island ponds

### 2024-07-19 manuscript/manuscript.qmd
Fresh render
MC revisions for BC STICS review

![Comparison of fluorometers by waterbody](images/fig2_chla_scatter.jpg){#fig-chlascatter width="8.5in" height="5.25in"}

```{r chl_summary, results='asis', echo=FALSE, message=FALSE}
#| label: tbl-chlsummary
#| tbl-cap: "Extracted chlorophyll summary data by waterbody and instrument."

knitr::kable(fluoro_summary$chl_summary)
```

@@

![Comparison of phycocyanin measurements by waterbody](images/fig3_phyco_scatter.jpg){#fig-phycoscatter width="8.5in" height="5.25in"}

```{r phyco_summary, results='asis', echo=FALSE, message=FALSE}
#| label: tbl-phycosummary
#| tbl-cap: "Extracted phycocyanin summary data by waterbody and instrument."

knitr::kable(fluoro_summary$phyco_summary)
```

@@

!!! REWRITE ME - Changed from biov to cells/ml, only one fig now !!!! !!! Cyanobaceteria Cell Counts are natural units / mL !!!!

@@

![Compare fluorometer chlorophyll to cyanobacteria cell counts](images/fig5_chl_vs_cells.jpg){#fig-chlcount width="8.5in" height="5.25in"}

![Compare fluorometer phycocyanin to cyanobacteria cell counts](images/fig6_phyco_vs_cells.jpg){#fig-phycocount width="8.5in" height="5.25in"}

@@

```{r read_table1, echo=FALSE, message=FALSE}
library(dplyr)
library(readr)
table1 <- read_csv(here::here("data/cleaned_phycotech_cyano_data.csv")) %>%
  select(-family) %>%
  mutate(biovolume = round(biovolume, 1),
         relative_biovolume = round(relative_biovolume, 5))
```

```{r show_table1, results='asis', echo=FALSE}
#| label: tbl-supp
#| tbl-cap: "Waterbody, Cyano Genus, Relative Biovolume Total Biovolume"

knitr::kable(table1)
```

>>>>

![Comparison of fluorometer measurements of chlorophyll by waterbody.  Blue lines represent the best fit regression line.  R^2^ on plot is the coeffecient of determination for this line.](images/fig2_chla_scatter.jpg){#fig-chlascatter width="8.5in" height="5.25in"}

```{r chl_summary, results='asis', echo=FALSE, message=FALSE}
#| label: tbl-chlsummary
#| tbl-cap: "Summary of extracted chlorophyll from Turner Trilogy by waterbody."

knitr::kable(fluoro_summary$chl_summary, row.names = FALSE)
```

@@

![Comparison of fluorometer measurements of phycocyanin by waterbody.  Blue lines represent the best fit regression line.  R^2^ on plot is the coeffecient of determination for this line.](images/fig3_phyco_scatter.jpg){#fig-phycoscatter width="8.5in" height="5.25in"}

```{r phyco_summary, results='asis', echo=FALSE, message=FALSE}
#| label: tbl-phycosummary
#| tbl-cap: "Summary of extracted phycocyanin from Turner Trilogy by waterbody."

knitr::kable(fluoro_summary$phyco_summary, row.names = FALSE)
```

@@

@@

![Compare fluorometer chlorophyll to cyanobacteria cell counts. Blue lines represent the best fit regression line.  R^2^ on plot is the coeffecient of determination for this line.](images/fig5_chl_vs_cells.jpg){#fig-chlcount width="8.5in" height="5.25in"}

![Compare fluorometer phycocyanin to cyanobacteria cell counts. Blue lines represent the best fit regression line.  R^2^ on plot is the coeffecient of determination for this line.](images/fig6_phyco_vs_cells.jpg){#fig-phycocount width="8.5in" height="5.25in"}

@@

```{r read_table1, echo=FALSE, message=FALSE}
library(dplyr)
library(readr)
table1 <- read_csv(here::here("data/cleaned_phycotech_cyano_data.csv")) %>%
    select(-family) %>%
    mutate(biovolume = round(biovolume, 1),
           relative_biovolume = round(relative_biovolume, 5)) %>%
    filter(waterbody %in% c("Barber Pond", "JL Curran Reservoir", "Indian Lake", "Mashapaug Pond", "Warwick Pond", "Yawgoo"))
```

```{r show_table1, results='asis', echo=FALSE}
#| label: tbl-supp
#| tbl-cap: "Cyanobacteria community composition by genus and waterbody, including total biovolume and relative biovolume."

knitr::kable(table1, row.names = FALSE)
```
